Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-01-04 paper.tex
update conclusions

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based context-BMC for full C programs (ESBMC)~\cite{Cordeiro12}, which was later extended to C++ programs~\cite{ECBS13}. \textbf{(RP2)} This approach was further developed and extended to verify deadlock, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}. These verification methodologies and respective tools were also able to find undiscovered bugs related to arithmetic overflow, buffer overflow, and invalid pointer in standard benchmarks, which were confirmed by the benchmark's creators ({\it e.g.}, NOKIA, NEC, NXP, and VERISEC). \textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated, demonstrating is effectiveness in real-life embedded applications~\cite{Gadelha15,Rocha15}. \textbf{(RP4)} The SMT-based context-BMC was also extended to verify overflow, limit cycle, time constraints, stability, and minimum phase in discrete-time systems ({\it e.g.}, digital filters and controllers)~\cite{dsv_spin2015,esbmc_controller,esbmc_filter}. Last but not least, ESBMC represents one of the most prominent BMC tools in the international software verification competition~\cite{MorseCNF13,MorseRCN014}.

@@

This paper presented the main challenges to verify design correctness in embedded systems. In particular, stringent constraints imposed by the hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered during verification. Additionally, there is little evidence that model checking embedded software using \textit{k}-induction (and invariants) can be applied to formally verify the correctness and the timeliness of embedded systems. Given that the complexity of software has increased significantly in embedded products, there are still some (recent) advances to stress and cover exhaustively the state space of the system, in order to verify low-level properties that have to meet the application's deadline, access the memory region, handle concurrency, and control the hardware registers. As future work, the main goal of this research is to extend BMC as a design and verification tool for achieving a correct-by-construction embedded systems implementation; special attention will be given to modern micro-grids, considering small-scale versions of a centralized electricity system so that reliability and carbon emission reduction are amenable to verification.

@@

>>>>

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs (ESBMC)~\cite{Cordeiro12}, which was later extended to C++98 programs~\cite{ECBS13}. \textbf{(RP2)} This SMT-based BMC approach was further developed to verify deadlock, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering partial-order reduction and state-hashing techniques to prune the state-space exploration~\cite{morse15}. These verification methodologies and respective tools were also able to find undiscovered bugs related to arithmetic overflow, buffer overflow, and invalid pointer in standard benchmarks, which were confirmed by the benchmark's creators ({\it e.g.}, NOKIA, NEC, NXP, and VERISEC). \textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated, demonstrating is effectiveness in some real-life embedded systems applications~\cite{Gadelha15,Rocha15}. \textbf{(RP4)} The proposed SMT-based context-BMC was also extended to verify overflow, limit cycle, time constraints, stability, and minimum phase in discrete-time systems, in particular, digital filters and controllers~\cite{dsv_spin2015,esbmc_controller,esbmc_filter}. Lastly, yet importantly, ESBMC represents one of the most prominent BMC tools (for verifying embedded systems) as observed in the international software verification competitions~\cite{MorseCNF13,MorseRCN014}.

@@

This paper presented the main challenges to verify design correctness in embedded systems. In particular, it emphasizes that stringent constraints imposed by the hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered during verification. Additionally, there is little evidence that model checking embedded software using \textit{k}-induction (and invariants), which
extends BMC-based approaches from falsification to verification, can be applied to formally verify the correctness and the timeliness of embedded systems. Given that the complexity of software has increased significantly in embedded products, there are still some (recent) advances to stress and cover exhaustively the state space of the system, in order to verify low-level properties that have to meet the application's deadline, access the memory region, handle concurrency, and control the hardware registers. As future work, the main goal of this research is to extend BMC as a design and verification tool for achieving a correct-by-construction embedded systems implementation; special attention will be given to cyber-physical systems and modern micro-grids, considering small-scale versions of a distributed system so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification.

@@

\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.
